Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-11-01 Manuscript/manuscript.tex
Update the methods text

\todo{SAMULI: Short discussion about mixtures should be added by citing the NMRlipids IV.}
The structures of lipid bilayers in simulations without ions were validated against NMR 
by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating the scattering form factors
as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
(see next section and Fig.~\ref{simVSexpNOions_POPS}).

Ion binding to lipid bilayers can be experimentally quantified
by measuring the changes of the head group order parameters in the lipids using solid state NMR.
In the case of the head group order parameters $S^\alpha$ and $S^\beta$ in phosphatidylcholine
(see Fig.~\ref{simVSexpNOions_POPS} for the definition of the order parameters)
such changes are known under the term ''electrometer concept'' \citep{seelig87,catte16, ollila16, melcr18, nmrlipids_proj4}. 
It is experimentally observed that the \ce{C-H} bond
order parameters of $S^\alpha$ and $S^\beta$ carbons in a PC lipid head group
are proportional to the amount of charge, positive or negative, bound per lipid~\citep{seelig87, roux90}.
The change of the order parameters measured with varying concentrations of aqueous ions 
can be then related to the amount of bound ions.

@@

MD simulations were performed using the GROMACS 2018 \cite{Abraham15} simulation package. 
The simulated system consisted of lipids (POPC and POPS) forming a single lipid bilayer,
an amount of water molecules comparable to the hydration levels in experiments, 
\todo{Check this claim. SAMULI: Check discussin in the NMRlipids IV manuscript}
and concentrations of ions (\ce{K^+}, \ce{Na^+}, \ce{Ca^{2+}} and \ce{Cl^{-}})
in an orthorhombic simulation box with periodic boundary conditions. 
The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}. 
A comprehensive list of simulations used in this work is in Table~\ref{tbl:sim-list}.

We used the SPC/E~\cite{Berendsen1987} water model \todo{SAMULI: The choice of water model should be justified.}
and ECC-ions \cite{martinek17, kohagen16, Pluharova2014} 
for the simulations with ECC-lipids.
Force field parameters for POPC were taken from Ref.~\citenum{melcr18}. 
The ECC-POPS model as derived again from the Lipid14
\todo{SAMULI: References to Lipid14/Lipid17 models should be consistent here and elsewhere.
We could also consider using term Amber lipd force field.}
force field~\cite{dickson14, lipid17-future}, as was described above.
For a direct comparison, 
we also performed simulations with the Lipid14
\todo{SAMULI: Also Lipid17 is used. The origin of Gromacs suitable files (Zenodo, acpype, etc.) should be described.}
model~\cite{dickson14},
the TIP3P water model~\cite{jorgensen83}, 
and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006}.
\todo{The usage of Dang ions should be justified here.}

For deposited trajectories and parameter files see Refs.~
\todo{Joe: Upload trajectories and add references here.}

>>>>

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as an error bar \cite{botan15,,ollila16,nmrlipids_proj4}.

Cation binding affinity to phosphatidylcholine (PC) lipid bilayers can be evaluated using 
the order parameters of $\alpha$ and $\beta$ carbons in the lipid headgroup 
(see Fig.~\ref{simVSexpNOions_POPS} for the labeling
\todo{SAMULI: Currently the figure has only PS structure while we use PC also in this work.
We should either add also PC structure or refer to somewhere else for the labeling.}) \cite{catte16}.
According to the ''electrometer concept'' \citep{seelig87}, these order parameters decrease
proportionally to the bound charge and can therefore be used to quantify the cation binding
affinity to PC lipid bilayers. The situation is more complicated for lipid bilayers containing
PS lipids because the ion free reference state does not exist due to the counterions and additional
ions often lead to phase transitions \cite{nmrlipids_proj4,feigenson86,mattai89,roux91,roux90}
Here, we overcome these complications by comparing simulations to the experimental data measured
from POPC:POPS (5:1) mixtures with additional ions\cite{roux90}, as demonstrated in the
recent work by the NMRlipids project \cite{nmrlipids_proj4}.

%experimentally quantified
%by measuring the changes of the head group order parameters in the lipids using solid state NMR.
%In the case of 
%such changes are known under the term 
%It is experimentally observed that the \ce{C-H} bond
%order parameters of $S^\alpha$ and $S^\beta$ carbons in a PC lipid head group
%are proportional to the amount of charge, positive or negative, bound per lipid~\citep{seelig87, roux90}.
%The change of the order parameters measured with varying concentrations of aqueous ions 
%can be then related to the amount of bound ions.

@@

MD simulations of POPC:POPS lipid bilayers with different molar ratios 
and ion concentrations (\ce{K^+}, \ce{Na^+}, \ce{Ca^{2+}} and \ce{Cl^{-}})
were performed in an orthorhombic simulation box with periodic boundary conditions
using the GROMACS 2018 \cite{Abraham15} simulation package. 
%The simulated system consisted of lipids (POPC and POPS) forming a single lipid bilayer,
%an amount of water molecules comparable to the hydration levels in experiments, 
%\todo{Check this claim. SAMULI: Check discussin in the NMRlipids IV manuscript}
The simulated systems are listed in Table~\ref{tbl:sim-list} and the used parameters
in Table~\ref{tbl:mdpar}. 
\todo{SAMULI: All the simulations were ran ?? ns and the first ?? ns were omitted as
an equilibration period. Or some other description of simulation times and equlibration.}
For deposited trajectories and parameter files see Refs.~
\todo{Joe: Upload trajectories and add references here.}

In the reference simulations with the standard Amber force field,
we used the Lipid14 parameters~\cite{dickson14} for POPC, the Lipid17 parameters for POPS \cite{gould18},
the TIP3P water model~\cite{jorgensen83}, and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006}.
The Lipid14 parameters in Gromacs format were downloaded from ?? \todo{SAMULI: Add this} and
the Lipid17 parameters were \todo{SAMULI: Describe how lipid17 parameters in Gromacs were generated.}.
The ion model by Dang and coworkers was used in these simulations because
the default ion parameters in Amber exhibit clustering in solution with relatively
low concentrations which complicates the evaluation of binding affinity against experiments \cite{nmrlipids_proj4}.
We used the SPC/E~\cite{Berendsen1987} water model \todo{SAMULI: The choice of water model should be justified.}
and ECC-ions \cite{martinek17, kohagen16, Pluharova2014} 
for the simulations with ECC-lipids.
Force field parameters for POPC were taken from Ref.~\citenum{melcr18}. 
The ECC-POPS model as derived again from the Lipid14
\todo{SAMULI: References to Lipid14/Lipid17 models should be consistent here and elsewhere.
We could also consider using term Amber lipd force field.}
force field~\cite{dickson14, lipid17-future}, as was described above.
